---
title: "Explicit Timecourse"
output: html_notebook
---

# Overview
When participants experience a cursor rotation while making a reach to a target, they must compensate by deviating their hand movement in order to get a cursor straight to its target.  

In this experiment, participants learned to counter a rotation and were instructed to report their aiming strategy by changing the direction of an arrow. 

Rotation sizes introduced were 20, 30, 40, 50, and 60 degrees.

<br>

# Data
We will be exploring:
<br>1. The proportion of learners within each perturbation condition.
<br>2. The proportion of aiming strategies as a function of rotation size.
<br>3. The onset of an aiming strategy as a function of rotation size.
<br>4. The magnitude of the aiming strategy as a function of rotation size.

# Setup

Get necessary packages:
```{r}
library('remotes')
ip <- installed.packages()
if ('Reach' %in% ip[,'Package']) {
  if (ip[which(ip[,'Package'] == 'Reach'),'Version'] < "2025.02.16") {
    remotes::install_github('thartbm/Reach')
  }
} else {
  remotes::install_github('thartbm/Reach')
}
```

Source project code:

```{r}
# download and handle data:
source('R/')
# scripts for group 2:
source('R/')
```

## Analysis Steps - Visualization


### Learning
Did all participants learn to counter the pertuburtation at least 50% of the time?


### Aiming Strategy Proportion
Did all learners have a strategy (ie, deviate their aim)? 
<br>Did the number of strategies vary as a function of rotation size.


### Aiming Strategy Onset
At what trial did participants begin deviating their hand reach (in the opposite direction of the rotation)?
<br>At what trial did participants begin deviating their explicit aim?
<br>Did the magnitude in aim change increase with larger rotation sizes?

<br>

## Analysis Steps - Statistics

### Oneway ANOVA
Does the proportion of participants who make a step differ across rotation sizes?
<br>Does the average step size differ between rotation sizes?
<br>Does the average trial at which the step occurs differ across rotation sizes?

### Bayesian ANOVA
A large Bayesian Factor (>10) suggests strong evidence for a difference.